cardinalR: Generating interesting high-dimensional data structures

### 2025-05-19 paper-cardinalR.tex
Fixed the mathematical formula issue

\(X_{1} \sim U(0.1, 2)\): base variable (avoids zero to prevent division errors).
\(X_{3} \sim U(0.1, 0.8)\): independent auxiliary variable.

:non-linear combination of \textbf{hyperbolic and sinusoidal transformations}, creating sharp curvature and oscillation.
\(X_{4} = \cos(\pi \cdot X_{1}) + \varepsilon\), with \(\varepsilon \sim U(-0.1, 0.1)\): additional nonlinear variation based on cosine, simulating more subtle periodic structure.

>>>>

\(X_{1} \sim U(0.1, 2)\): base variable (avoids zero to prevent division errors).
\(X_{3} \sim U(0.1, 0.8)\): independent auxiliary variable.
\(X_{2} = \frac{hc}{X_{1}} + \text{nonfac} \cdot \sin(X_{1})\): non-linear combination of \textbf{hyperbolic and sinusoidal transformations}, creating sharp curvature and oscillation.
\(X_{4} = \cos(\pi \cdot X_{1}) + \varepsilon\), with \(\varepsilon \sim U(-0.1, 0.1)\): additional nonlinear variation based on cosine, simulating more subtle periodic structure.
